Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-16 paper/main.tex
auto deployment

\subsection{Whole infrastructure}

@@

>>>>

\subsection{Whole infrastructure and automatic deployment}

@@

To speed up the development of the demo, automatic deployment has been built from the first day. There are two types of deployment scripts. The first type is shown 
as Fig.~\ref{ansible}, which is built by Ansible. The entire basic environment can be built from this directory. Below steps can build a clean deployment for this demo.

\begin{itemize}
    \item Ensure that the local aws-cli configuration is ready to use, i.e running "aws configure".
    \item Run "ansible-playbook -v -i hosts2 supervisor.yml" to generated a new EC2. Get the IP address.
    \item Run "ssh -i ~/.ssh/[key] root@[ip]" to login.
    \item Run "git clone https://github.com/A2/A2.git" to get the code.
    \item Install the basic requirements and initial part as the README.md under the "deploy" directory.
    \item When requirements are ready, running "ansible-playbook -v -i hosts site.yml" will deploy the all of the services including Tomcat, Nginx, ELB, Java. 
\end{itemize}

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/ansible.png}}
    \caption{Deployment By Ansible}
    \label{ansible}
\end{figure}

The second type of deployment is shown as Fig.~\ref{cf1}, which is built by CloudFormation. In Fig.~\ref{cf1}, there are the CloudFormation configuration files. 
Running "make deploy" in this directory will follow below steps to built the Lambda functions.

\begin{itemize}
    \item Generate a role named lmdRole and attach various access rights.
    \item Generate some SQS queue for the Lambda fucntions.
    \item Define the functions and bind the role, handlers, queues, configurations.
\end{itemize}

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/cf-1.png}}
    \caption{Deployment of imagery process}
    \label{cf1}
\end{figure}

Running "make deploy" in the directory show as Fig.~\ref{cf2}, which is "A2/deploy/roles/mysql/templates", can create a slave RDS MySQL instance. Because 
a cross-region database replica is needed in this demo, running "make master" can build another master RDS MySQL after changing the aws-cli region. And the 
slave instance is replicated instantly from the master instance. Both of the commands for MySQL are using CloudFormation. The first one is just a very 
simple process, but the second one is also generating a Lambda function to rotate the MySQL password in the master database, and store it in Secrets Manager service.

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/cf-2.png}}
    \caption{deployment of MySQL}
    \label{cf2}
\end{figure}

After above steps, the entire demo should be ready for processing s3 imagery and users can visit it from the ELB URL.
